### 2015-06-09 text/ms.Rmd
Add to text and bibliography

Ensemble models, which combine the output from multiple models, are one
potential solution to this problem. A simple ensemble model might take the
average of multiple model outputs, perhaps weighted by some goodness of fit
(REFs). A complex ensemble model might also take into account the interactions
between model outputs and additional covariates. Ensemble models are popular in
many fields including public health [e.g. @thomson2006], agriculture [e.g.
@cantelaube2005], climate science (e.g. REFs), and machine learning (e.g.
REFs). We think they have tremendous opportunity in ecological resource
management.

In fisheries science, a common problem is estimating the status of an exploited
fish population. For the majority of fish stocks, we have limited biological
information and stock status isn't known (e.g. REFs).  In recent years, a
number of methods have been proposed to derive population status based on the
limited information that is frequently available: fisheries catch time series
and basic knowledge about the productivity of the species. Recent work has
investigated the ability for these models to estimate population status through
a large-scale simulation model [@rosenberg2014]. A key finding was that these
models frequently disagree on population status and any one model has
relatively poor predictive ability (e.g. Fig. \ref{fig:motivate}).

@@

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $b$ is the true value the model is
fitted to, $S(n)$ represents the spectral density at frequency $n$ of the
scaled catch series, and $\theta$ is the set of parameters for the regression
function. For all ensemble models of mean \bbmsy\\, which is bounded at zero,
we fit the models in log space and exponentiated the predictions to derive a
median estimate of \bbmsy\\. For the estimates of \bbmsy\\ slope we fit
ensemble models on the natural untransformed scale.

@@

Funding...

>>>>

Ensemble models, which combine the output from multiple models, are one
potential solution to this problem. A simple ensemble model might take the
average of multiple model outputs, perhaps weighted by some goodness of fit. A
complex ensemble model might also take into account the interactions between
model outputs and additional covariates. Ensemble models are popular in other
fields including public health [e.g. @thomson2006], agriculture [e.g.
@cantelaube2005], climate science [e.g. @murphy2004; @tebaldi2007;
@pierce2009], and machine learning [e.g. @dietterich2000]. We think they have
tremendous opportunity in ecological resource management.

In fisheries science, a common problem is estimating the status of an exploited
fish population. For the majority of fish stocks, we have limited biological
information and stock status isn't known [@fao2014]. In recent years, a number
of methods have been proposed to derive population status based on the limited
information that is frequently available: fisheries catch time series and basic
knowledge about the productivity of the species. Recently, @rosenberg2014
investigated the ability for these models to estimate population status through
a large-scale simulation model. A key finding was that these models frequently
disagree on population status and any one model has relatively poor predictive
ability (e.g. Fig. \ref{fig:motivate}).

@@

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(n)$ represents the spectral density
at frequency $n$ of the scaled catch series, $b$ is the true value the model is
fitted to, and $\theta$ is the set of parameters for the regression function.
For all ensemble models of mean \bbmsy\\, which is bounded at zero, we fit the
models in log space and exponentiated the predictions to derive a median
estimate of \bbmsy\\. For the estimates of \bbmsy\\ slope we fit ensemble
models on the natural untransformed scale.

@@

<!--Funding...-->
